\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{20pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!50!red,
    linkbordercolor=red,
    urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
    \item\small{
        \ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
    }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & \textcolor{mygray}{#2}                 \\
        \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}       & \textcolor{mygray}{#2}                 \\
        \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
        {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1}      & \textcolor{mygray}{#2}                 \\
        \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large Lev Chechulin} & Email : \href{mailto:fadyat@icloud.com}{lyovoch@bk.ru} \\
Github: \href{https://github.com/jizapika}{jizapika} & Mobile : +7\hspace{0.5ex}999\hspace{0.5ex}232\hspace{0.5ex}32\hspace{0.5ex}70 \\
\end{tabular*}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National Research University ITMO}
{Saint-Petersburg, Russia}
{Information systems and technologies}
{Sept. 2020 - Aug. 2024 (Present)}
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart

\resumeProjSubheading
{\href{https://github.com/jizapika/CarShop}{Car Shop}}{}
{\skill{Java} \skill{Spring} \skill{postgres} \skill{JPA}}{Dec. 2022}
\resumeDesc{
Learned the Spring Boot framework. Work with DataBase (postgres) using JPA. \\
Application contains the autorization and registration of car sellers. \\
It also provides an API for finding cars by color.
}

\resumeProjSubheading
{\href{https://github.com/is-tech-y24-1/jizapika/tree/master/2laba}{Client Generator}}{}
{\skill{C\#} \skill{Java} \skill{Roslyn} \skill{LINQ}}{Sept. 2022}
\resumeDesc{
For the Java server, a C\# client is generated using Roslyn. \\
Implemented a parser for the model and controllers into a syntax tree.\\
And then a C\# client is created using it.
}

\resumeProjSubheading
{\href{https://github.com/is-tech-y24-1/jizapika/tree/lab-3}{Code fixer and analyzer}}{}
{\skill{C\#} \skill{Roslyn} \skill{LINQ}}{May 2022}
\resumeDesc{
The analyzer finds methods that have the Try prefix in their name and issues a warning if a non-bool value is returned. \\
After acceptance, code fixer performs a signature substitution so that it returns a bool + out parameter. \\
It was developed using the Roslyn parser and abstract syntax tree parsing.
}

\resumeProjSubheading
{\href{https://github.com/is-oop-y24/jizapika/tree/master/Reports}{Reports}}{}
{\skill{C\#}\skill{Swagger}}{Mar. 2022}
\resumeDesc{
A server application with a multi-layer architecture has been implemented, providing an API for working with the reporting system in team development. \\
Used Swagger for testing functionality. \\
Implemented a Data Access Layer with using Entity Framework.
}

\resumeProjSubheading
{\href{https://github.com/is-oop-y24/jizapika/tree/master/Banks}{Bank System}}{}
{\skill{C\#}}{Dec. 2021}
\resumeDesc{
Banking system with UI. The central bank controls all transactions. There are accounts and clients for each bank.
}

\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart

\resumeProjSubheading
{{Tinkoff Java course. Spring 2023.}}{}
{\skill{Java}}
{Mar. - May 2023}
\resumeDesc{}

\resumeProjSubheading
{{Competitive Programming}}{}
{\skill{C++}\skill{Algorithms and data structure}}
{2016 - 2020}
\resumeDesc{
{\href{https://neerc.ifmo.ru/archive/2020/northern/standings.html}
{ICPC(45 place)}},
{\href{https://codeforces.com/profile/jizapika}
{Codeforces (2100)}}
}

\resumeProjSubheading
{{Regional Olympics}}{}{\skill{Critical thinking}}{}
\resumeDesc{
Math (2014-2020), Physics (2016-2018), Programming (2017-2020)
}

\resumeSubHeadingListEnd

\section{Programming Skills}
\resumeSubHeadingListStart
\item{
\textbf{Languages}{: C++, C\#, Java, Python}
}\vspace{-7pt}
\item{
\textbf{Technologies}{: SQL, Git, Bash, Maven }
}
\vspace{-7pt}
\item{
\textbf{Knowledge}{: Algorithms, Data Structures, Operating Systems, Databases, Object-Oriented Programming, Machine Learning}
}
\resumeSubHeadingListEnd

\end{document}
